### 2018-07-18 paper/conclusion.tex
Moves Adrien's old future work back to conclusion
It's not security, so I'll put it back where it was until we know where
it should be.

We presented \name that, in analogy to its biological
counterparts, enables dissemination under unfavorable conditions. More
specifially, the deliberate dissemination of files without using
storage on third-party devices, be they peers or servers in the
cloud. This constraint results in the unfavorable conditions of
reduced a-priori availability and therefore unreliable nodes for
routing. We build resilience to these conditions by using predictive
modeling for user behavior and the ensuing availability of their
devices. From our experiments, we find that even suboptimal prediction
already results in successful file transfer with high probability,
though often at low speed. More in-depth knowledge of the users'
behavior would allow us to predict device connectivity farther into
the future and thus likely improve the throughput. From a security and
privacy perspective, we were guided by the properties of
TOR~\cite{Tor}, which we used to provide a modicum of privacy for this
first investigation of feasibility of file-sharing between two users'
squads of devices and modified to a stateless protocol to
accommodate unreliable nodes. While we took the first steps toward
analyzing the consequences of the modifications on security and
privacy, more work is needed to provably ensure that the added feature
of resilience despite unreliable nodes (supported by peer sampling)
and the side effect of enabling more local TOR routing (for example,
keeping routes inside a country) do not compromise security. Another
consideration is the nature of the traffic in this scenario and the
limits of protection against statistical inference. On a
related note, it would be interesting to adapt the
Sphinx~\cite{Sphinx} cryptographic packet format to the routing of
\name as a step toward provable security.

>>>>

We presented \name that, in analogy to its biological
counterparts, enables dissemination under unfavorable conditions. More
specifially, the deliberate dissemination of files without using
storage on third-party devices, be they peers or servers in the
cloud. This constraint results in the unfavorable conditions of
reduced a-priori availability and therefore unreliable nodes for
routing. We build resilience to these conditions by using predictive
modeling for user behavior and the ensuing availability of their
devices. From our experiments, we find that even suboptimal prediction
already results in successful file transfer with high probability,
though often at low speed. More in-depth knowledge of the users'
behavior would allow us to predict device connectivity farther into
the future and thus likely improve the throughput. From a security and
privacy perspective, we were guided by the properties of
TOR~\cite{Tor}, which we used to provide a modicum of privacy for this
first investigation of feasibility of file-sharing between two users'
squads of devices and modified to a stateless protocol to
accommodate unreliable nodes. While we took the first steps toward
analyzing the consequences of the modifications on security and
privacy, more work is needed to provably ensure that the added feature
of resilience despite unreliable nodes (supported by peer sampling)
does 
%and the side effect of enabling more local TOR routing (for example,
%keeping routes inside a country) do 
not compromise security. Another
consideration is the nature of the traffic in this scenario and the
limits of protection against statistical inference. 
%On a related note, it would be interesting to adapt the
%Sphinx~\cite{Sphinx} cryptographic packet format to the routing of \name as a step toward provable security.

%
% \commentAL{To rewrite as real paragraphs} Future work and prospects:
% \begin{itemize}
% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
% 	\item Changing devices' asymmetric keys regularly would increase security.
% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver. To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.

% \end{itemize}

### 2018-07-18 paper/design.tex

This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ 
through \name; they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

>>>>

This section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They categorize anonymous communication protocols using the following 
categories:
\begin{description}
  \item[Network structure]
    This describes the characteristics of the anonymous relays, the connections 
    between them and the underlying topology.

  \item[Routing information]
    This describes the network information available to entities deciding on 
    the route of an anonymous connection.

  \item[Communication model]
    This describes the entities that make the routing decisions and how they 
    make these decisions.
\end{description}

We first describe Sphinxes, which is an adaptation of the Sphinx~\cite{Sphinx} 
mix-header format.
This affects very few parts of the taxonomy above.

Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ 
through \name; they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

### 2018-07-18 paper/evaluation.tex

\paragraph*{PORs creation}
Figure \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
$\theta$, the threshold of the probability that all nodes fail at once (cf. \ref{ssub:building_routes}), takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
The time since route establishment goes from 1 to 10 with  unit step.
It is measured in time periods $T$, the interval at which users change the connection state of their devices.
An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
Hence, each point on the top of figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
each point on the bottom is the availability rate over 200 routes.

@@

We now study the influence of the parameters on the future availability of the routes in figure~\ref{fig:success_rate_vs_t}.
We consider a route available if at least one node per layer is online at this time.
The plots reads the mean availability of routes as a function of the time since the route's establishment, for every couple of parameters $(\theta, L)$.
First of all, we observe that time has a negligible impact on the availability of routes. 
This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
We also see that $\theta$ has a big impact on the mean availability and its variability.
Still, $\theta\in\{10^-4, 10^-3\}$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
Combined with the results from figure~\ref{fig:nodes_per_layer_vs_theta}, it means that routes will need an average of 5-6 devices per layer to be highly available.
Finally, increasing $L$ logically hinders the results when using low-availability layers.
\\

>>>>

\paragraph*{PORs creation}
Figure \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
$\theta$, the threshold of the probability that all nodes fail at once, takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
The time since route establishment goes from 1 to 10 with  unit step.
It is measured in time periods $T$, the interval at which users change the connection state of their devices.
An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
Hence, each point on the top of figure~\ref{fig:success_rate_vs_t} is the average of 3000 layers size; 
each point on the bottom is the availability rate over 200 routes.

@@

We now study the influence of the parameters on the future availability of the routes in figure~\ref{fig:success_rate_vs_t}.
We consider a route available if at least one node per layer is online at this time.
The plots reads the mean availability of routes as a function of the time since the route's establishment, for every couple of parameters $(\theta, L)$.
First of all, we observe that time has a negligible impact on the availability of routes. 
This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
We also see that $\theta$ has a big impact on the mean availability and its variability.
Still, $\theta\in\{10^-4, 10^-3\}$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
Combined with the results from figure~\ref{fig:success_rate_vs_t}, it means that routes will need an average of 5-6 devices per layer to be highly available.
Finally, increasing $L$ logically hinders the results when using low-availability layers.
\\

### 2018-07-18 paper/global-overlay-design.tex
algo
Adds missing \pk

\subsection{The Global Overlay}
\label{sec:global_overlay}

\newcommand{\viewsize}{\ensuremath{l_{\text{view}}\xspace}}
\newcommand{\view}{\ensuremath{\mathcal{V}_{\text{RPS}}\xspace}}
\NewAlgorithm{\GetRandomPeer}{random descriptor from \view}

@@

>>>>

\NewScheme{\SPOR}{SPOR}

\subsection{\Acfp*{SPOR}}%
\label{sec:global_overlay}
\label{sec:message_passing}

Say that Alice wants to send a message \(m\) to Bob.
Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
over an out-of-band channel.
We assume that \(m\) is either unavailable when the channel is used or too 
large to successfully send over the channel directly.
At a later point, Alice attaches a message \(m\) to the reply header using 
\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
reply header as payload.
Then she sends this packet to the first node, which processes it using 
\(\ProcessHeader\).
The node will then process the header and in turn forward the packet to the 
next node.
At some point the message will reach Alice who identifies the message as the 
one expected to come from Bob.
(This process is illustrated in \cref{fig:file-exchange}.)
Now we will focus on how Alice and Bob choose the nodes that they provide to 
\(\CreateReply\) and \(\CreateFwd\).

\begin{figure}
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}%
    A schematic of Alice and Bob sending a message using \name.
    \ding{1} illustrates the layer of the headers that Alice and Bob create.
    In \ding{2}, Alice and Bob exchange the headers out-of-band.
    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
    one for acknowledgements.
  }
\end{figure}

There are many uses of Sphinxes, many criteria that can be used to select the 
nodes in each layer.
We will focus on maximizing availability when routing in a network with high 
churn, but one could equally well select nodes to maximize, \eg, bandwidth.
We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
from a source to a destination over a network of nodes with high churn.

\commentDaniel{We should describe how to do this selection using a prediction 
  oracle, then we provide a prediction oracle later.}
\commentDaniel{The stuff below is just as before, it must be edited.}

\newcommand{\viewsize}{\ensuremath{l_{\text{view}}\xspace}}
\newcommand{\view}{\ensuremath{\mathcal{V}_{\text{RPS}}\xspace}}
\NewAlgorithm{\GetRandomPeer}{\text{random descriptor from }\view}

@@

\NewVariable{\pk}{pk}

### 2018-07-18 paper/intro.tex

Although data encryption is often proposed as a first line of defense for cloud-hosted data, it is unfortunately  insufficient~\cite{granick_2017, HooffLZZ15, HarnikPS10}. Metadata such as a user'
location and activity can still be tracked, including access
control histories, thus revealing what each user shared with whom and when. 
%  because it does not protect meta-data information
The exposure of metadata seriously weakens user privacy, as famously emphasized by a former NSA and CIA director: "\emph{We kill people based on metadata.}''~\cite{NaughtonTheGuardian2016} 
In this model, user devices, masquerading as allies, get turned into tracking and/or monitoring \squad{}s, and serve as highly efficient spies over their owners.

>>>>

Although data encryption is often proposed as a first line of defense for cloud-hosted data, it is unfortunately  insufficient~\cite{granick_2017, HooffLZZ15, HarnikPS10}. Metadata such as a user'
location and activity can still be tracked, including access
control histories, thus revealing what each user shared with whom and when. 
%  because it does not protect meta-data information
The exposure of metadata seriously weakens user privacy, as famously emphasized by a former NSA and CIA director: "\emph{We kill people based on metadata.}''~\cite{NaughtonTheGuardian2016} 
In this model, user devices, masquerading as allies, get turned into %% tracking and/or monitoring \squad{}s, and serve as
highly efficient spies over their owners.

### 2018-07-18 paper/related.tex

As a whole, \name is related to but differs from the following concepts: storage and sharing (cloud, P2P file sharing, P2P storage),  mixnets, and onion routing (with infrastructure or P2P).

>>>>

\name is designed to allow a user, say Alice,  to deliberately exchange files stored on any device of her e-squad with a specific other user, Bob, represented by any device belonging to his e-squad, without using any provider or storage other than on Alice or Bob's respective e-squads. As a whole, \name is related to but thus differs from the following concepts: storage and sharing (cloud, P2P file sharing, P2P storage),  mixnets, and onion routing (with infrastructure or P2P).
